---
title: | 
    | Notes on "Addressing Non-sincere Responses in Rank-Order Survey Questions"
    | (Atsusaka & Kim, 2023)
    | AU WiP
header-includes:
  - \usepackage{datetime}
  - \usepackage{natbib}
  - \usepackage{amsmath}
  - \usepackage{pifont}
  - \usepackage{wasysym}
  - \usepackage{color}
date: 2023-02-24\newline
      \newline
      $^1$American University\newline
author: 
  - Ryan T. Moore$^{1}$ 
output:
  beamer_presentation:
    slide_level: 2
    toc: true
    fonttheme: serif
    # includes:
    #   in_header: zzz_beamer_header.tex
  pdf_document:
    fig_caption: true
    number_sections: true
    urlcolor: blue
link-citations: yes 
bibliography: "../Documents/Dropbox/research/computing/bib/main.bib"
---

<!-- \setbeamertemplate{footline}[page number] -->
<!-- \newcommand{\begincols}[1]{\begin{columns}{#1}}  -->
<!-- \newcommand{\stopcols}{\end{columns}} -->
<!-- \usepackage[normalem]{ulem} -->
\newcommand{\independent}{\perp\mkern-9.5mu\perp}


```{r knitr options, echo=FALSE, warning=FALSE}
# Encoding required for proper knitr rendering
options(encoding = "native.enc")
```

```{r enviro, warning = FALSE, results = 'hide', echo = FALSE, message = FALSE}
# Load packages:
library(dplyr)
library(ggplot2)
library(png)
library(grid)
library(gridExtra)
library(modelr)
library(readr)
library(tibble)
library(tidyr)
```


# Big Picture

## Framing the Paper, Big Questions

\large

@atskim23

To what degree \ldots

>- is paper about _ranking_ specifically?
>    - (especially, item randomization)
>- is paper about attraction to _geometric or numeric patterns_ specifically?
>- should paper address other sources of non-sincerity?
>    - (strategy, indifference, ignorance, social desirability, \ldots)
>- should paper draw on insights/connections to other literatures?
>    - (missing data, sensitive items, conjoints, vignettes, doubly-robust methods)

\pause 

(Some of this for \S1, some for \S9, some for body)


## Sincerity

\large

What is _non-sincerity_?

\pause 

"responses that do not reflect people’s underlying preferences and are instead based on some patterns"

\pause 

"a non-sincere ranking, which can be anything but has no substantive meaning"

\pause 

>- Attraction to geometric patterns on response interface
>- Clarify "what patterns?"
>- Other question types (battery of Likerts, Approve/Disapproves, \ldots)

## Sincerity

\large

What could _non-sincerity_ be masking?

>- Strategic behavior
>    - (Will never rank my 2nd choice "2", since 3rd is no threat)
>- Systematic measurement error
>    - (Survey social desirability $\rightsquigarrow$ I "should" rank $C$ last \ldots)
>- Indifference 
>    - (Completeness and transitivity are assumed!)
>- Satisficing/Response to cognitive challenge
>    - (Completeness and transitivity are assumed!)
>- Dependence on alternatives ($ABC$, but $ADCB$)
>    - (Completeness and transitivity are assumed!)


# Connections

## Connection 1: Missing Data

\large

What is role of independence assumption? 

\setcounter{equation}{5}
\begin{eqnarray}
\pi_{i,s} \independent z_i & \text{ such that } &\mathbb{P}(\pi_{i,s} | z_i = 1) = \mathbb{P}(\pi_{i,s})
\end{eqnarray}

\pause 

In missing data, 

>- assume MCAR and life is easy  
(listwise deletion inefficient but unbiased)
>- assume the typical, realistic MAR or NI, and need more  
(multiple imputation)

## Connection 2: List Experiments for Sensitive Items

\large

What is role of independence assumption? 

\setcounter{equation}{5}
\begin{eqnarray}
\pi_{i,s} \independent z_i & \text{ such that } &\mathbb{P}(\pi_{i,s} | z_i = 1) = \mathbb{P}(\pi_{i,s})
\end{eqnarray}
\pause 

In sensitive items, whole point is *value* influences revelation

\pause 

How is your bias different from sensitive-item bias? 

>- You posit different psych source, but clarify this
>- Are list experiments (e.g.) just _pre-processing_?
>- (No, since applies to all respondents?)
>- (What is and is not _pre-processing_?)

## Connection 3: Conjoints

\large

Forced-choice conjoint designs are simple rankings.

\pause 

>- What assumptions, results can you import from conjoints?
>- Do your results inform conjoints?
>- Why don't conjoints randomize attribute order?
>    - Cognitive load

## Connection 4: Doubly-Robust Models

\large

\begin{eqnarray*}
\pi_i & \equiv & \pi_{i,s} z_i + \pi_{i,n} (1 - z_i) \qquad \qquad \qquad \qquad \qquad (2) \\
\mathbb{P}(\pi_{i,s} | z_i = 1) & = & \frac{\mathbb{P}(\pi_i) - (1 - Pr(z_i = 1)) \mathbb{P}(\pi_{i,n} | z_i = 0)}{Pr(z_i = 1)} \quad (4)
\end{eqnarray*}

\pause 

Beyond non-parametrics:

Model for response/ranking $+$ Model for sincerity

- @glyqui10 
- @tylgriwes22

## Connection 5: Anchoring Vignettes

\large

>- Surprising not to see connection to _anchoring vignettes_
>    - "Best est" $=f($ "Anchoring Qs" + "Correct w/ Anchors"$)$
>    - Several anchor Qs $\rightarrow$ one key response
>- "All interpret anchor same" $\approx$ "vignette equivalence"

\pause 

\vspace{5mm}

- @kinmursal04 
- @hopkin10

# Anchor Questions

## Anchor Questions

\large

What is an anchor question?  

- Deepen relationship betw'n **anchor** and **target** questions

\pause 

> "any respondent with minimal substantial knowledge can provide a correct ranking for the anchor question, irrespective of the heterogeneous underlying preferences"

\pause 

>- Develop this, to ensure it's plausible, not circular
>- How does this differ from an objective "attention check" like "president is state-level office-holder"?


## Anchor Questions

\large

Deepen relationship betw'n **anchor** and **target** questions

\pause 

Demonstrate

>- match between anchor and target works
>- match between anchor and target is required
>    - (Must I double survey length?)


## Anchor Questions

\large

>- Assumption 1: Target and anchor have same $Pr(\cdot)$ sincerity
>    - Strong?
>    - Factual vs. preference questions?
>- Assumption 2: there is only 1 insincerity
>    - Will capture a single constant geometry, but not sensitivity, ignorance, indifference, \ldots

\pause 

\vspace{3mm}

(Under assumptions, nice correction for "some get it right by chance" using item-order-randomization. But assumptions preclude anyone getting it wrong for any other reason.)

## Anchor Questions

Item-order randomization to estimate prop sincere

\footnotesize
\setcounter{equation}{8}
\begin{eqnarray}
\widehat{\text{Pr}}(z_i^{\text{anc}} = 1) & = & \left[ \frac{\sum_{i = 1}^N c_i}{N} - \frac{1}{J!} \right] \left(1 - \frac{1}{J!} \right)^{-1}
\end{eqnarray}

\pause 

\normalsize
>- Adjust for item-order imbalance? (confounds via primacy)
>- Unbiased, but does (9) do weird things? 
>    - no, if everyone gets it: $$\left(\frac{120}{120} - \frac{1}{6}\right)\left(1-\frac{1}{6}\right)^{-1} = 1$$
>    - no, if balance in anchor orders, etc: 
$$\left(\frac{20}{120} - \frac{1}{6}\right)\left(1-\frac{1}{6}\right)^{-1} = 0$$
>    - **yes**, if worse than that. E.g., everyone is wrong: 
$$\left(\frac{0}{120} - \frac{1}{6}\right)\left(1-\frac{1}{6}\right)^{-1} = -0.2$$


# Suggestions

## Suggestions

\large 

- \S5
    - Validate that nominal bootstrap coverage is correct
    - Bootstrap vs. inverting the RI-permutation test?
- \S8
    - What do I want to see? Not just with/without correction, but also examination of quality of correction (test multiple anchors, other assumptions)


## Small Suggestions

- \S1
    - "Indeed, our survey data show that non-sincere responses are prevalent in rank-order questions regardless of their contexts" (p. 1)
    - If this refers to contextless response practice, it does not follow. "regardless" $\neq$ "in absence of".
- \S4.3 \smiley 
    - Add "No difference between sincere/insincere distributions"
- \S5
   - Can you test anchor questions to estimate how easy they are? (E.g., in a big class, with incentives for correctness to set an upper bound)
   - "and re-designing": what do you have in mind?

## Small Suggestions

- \S6
    - Show us table of three $\chi^2$ tests
- \S7
    - If replicate this, add "Option 1" to reflect real task
    - "we may expect respondents to uniformly choose a ranking pattern available in the $J!$ permutation space". Well, clearly not. Phrase as null hypothesis.
    - Add respondent count  
    (E.g., if $n = 100$, $J = 3$, then $p = 0.32$ !)




```{r fig.height=6, echo=FALSE, eval=FALSE}
img <- readPNG("three_pictures.png")
grid.raster(img)
```

<!-- \center -->
<!-- \includegraphics[width=3in]{figs/dot.pdf} -->

## References {.allowframebreaks}

\footnotesize

